---
title: "portfolio"
description: |
  Samples of my research and independent projects on topics like modelling tick population and infection dynamics, using remote sensing data to assess road infrastructure, and investigating biases in digital natural history collections.
output: 
  distill::distill_article:
    css: theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include=FALSE}
library(htmltools)
source("R/functions.R")
```

```{r}
create_proj_card(
  img_src = "images/ticks.png",
  url = "https://CRAN.R-project.org/package=IxPopDyMod",
  title = "Modelling tick populations",
  text = "Tick population models aid in assessing how climate change impacts disease risk, and in designing tick control strategies. While models exist in the literature, source code is often unavailable, making models difficult to compare. With Middlebury Professor David Allen, I developed IxPopDyMod, a flexible R package for running such models and comparing outputs in different scenarios. More soon - we're currently drafting a manuscript presenting the package.
",
  text2 = ""
)
```


```{r}
create_proj_card(
  img_src = "",
  url = "https://aves.shinyapps.io/optimalBigDay/",
  title = "Optimal Big Day",
  text = "Big Day is a global bird watching phenomenon in which birders try to observe the highest possible number of species within a 24 hour period. I co-developed an R Shiny app that uses eBird data in a probablistic model to predict optimal birding routes.
",
  text2 = ""
)
```

```{r}
create_proj_card(
  img_src = "",
  url = "http://comments.amnat.org/2021/01/call-for-special-topics-paper.html/",
  title = "Colonial legacies influence biodiversity lessons",
  text = "Caribbean natural history collections hold rich biological information. They also reflect how colonial history has influenced research trajectories in the region. I tailored analyses and visualizations of biodiversity data from GBIF to address research questions posed by collaborators in Tobago and the US. This work is part of a manuscript currently in review for the invited issue of The American Naturalist, Nature, Data and Power: How hegemonies shape biological knowledge.",
  text2 = ""
)
```


```{r}
create_proj_card(
  img_src = "images/montana.png",
  url = "https://mstokowski.users.earthengine.app/view/aismodel",
  title = "Predicting aquatic invasive species habitat suitability",
  text = "Tracking the spread of aquatic invasive species is key for informing management plans. At the Flathead Lake Biological Station, I built a Google Earth Engine web map for running a machine learning model that predicts invasive species habitat suitability.",
  text2 = ""
)
```

```{r}
create_proj_card(
  img_src = "images/middsense_map.png",
  url = "https://github.com/Middsense/pre-processing",
  title = "Middsense",
  text = "Manual approaches for detecting changes in road pavement quality are expensive and inefficient. In Professor Andrea Vaccari's lab at Middlebury, I investigated an alternative approach. The automated geospatial Python pipeline I co-developed extracts and processes synthetic aperature data along roads, for comparison with ground truth road quality data.",
  text2 = ""
)
